---
title: "odi batting"
author: "Dinesh Reddy"
date: "27 January 2017"
output: html_document
---
```{r}
library(ggplot2)
library(dplyr)
```
## Importing odi dataset
```{r}
odi.batting.analysis <- read.csv("D:/Nandan Pendrive/APTITUDE/Aptitude Books/MANIPAL DATA SCIENCE - TERM-2/DATA VISUALIZATION/odi-batting-analysis.csv")
   View(odi.batting.analysis)
 head(odi.batting.analysis)
 class(odi.batting.analysis)
```
## getting dimensions i.e how many rows and columns
```{r}
dim(filter(odi.batting.analysis,Player=="Sachin R Tendulkar"))
dim(filter(odi.batting.analysis,Player=="Aamer Hanif"))
dim(filter(odi.batting.analysis,Player=="Sachin R Tendulkar" | Player=="Aamer Hanif"))
```
## selecting column names
```{r}
 names(select(odi.batting.analysis,Country, Player, Runs))
 names(select(odi.batting.analysis,-Ground, -ScoreRate))
```
## Filtering a player from a column and summarising his runs
```{r}
sachin= filter(odi.batting.analysis, Player=="Sachin R Tendulkar")
 sachin %>% summarise(sum(Runs))
 summary<-sachin %>% summarise(mean(Runs))
```
## To write the  column name
```{r}
summary<-sachin %>% summarise(TotalRuns=sum(Runs), Avgrun=mean(Runs))
summary
class(summary)
```
## How many Total runs India made and their average
```{r}
 india=filter(odi.batting.analysis,Country=="India")
 indiaruns<- india %>% summarise(TotalRuns=sum(Runs),Avgrun=mean(Runs))
 indiaruns
```
## Total runs made by every country and their average
```{r}
 a<-odi.batting.analysis %>% group_by(Country) %>% summarize(TotalRuns=sum(Runs))
 a
 b<- odi.batting.analysis %>% group_by(Country) %>% summarize(TotalRuns=sum(Runs),Avgrun=mean(Runs))
b 
```
## using ggplot plotting  a bar graph , coord_flip will change the graph to vertical or horizontal
```{r}
g<-ggplot(data=b,mapping = aes(x=Country,y=TotalRuns,fill=Avgrun))+geom_bar(stat = "identity")+coord_flip()
g 
```
## plotting a histogram
```{r}
ggplot(odi.batting.analysis,aes(x=Runs))+geom_histogram()
```
